Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2018-02-14 paper-ieee-trans.tex
Fix reference

{\sl INDIGO--DataCloud} software stack is delivered in form of Linux software packages (rpms, debs)
and Docker containers. The CD approach is different for each type of software packaging. \textit{Linux
package pipeline} intentionally delivers the packages produced in a pre-production -- preview --
branch. Before that, once the software packages have been created, they are uploaded to a
testing branch. The available automated deployment solution -- see \cite{subsec:sqa} -- checks
the installation and configuration of the component relying on the testing repository. On
successful completion, the packages are then automatically signed and subsequently moved to
the preview branch, from where they finally be made available in the production branch after
the release manager supervises the process.

>>>>

{\sl INDIGO--DataCloud} software stack is delivered in form of Linux software packages (rpms, debs)
and Docker containers. The CD approach is different for each type of software packaging. \textit{Linux
package pipeline} intentionally delivers the packages produced in a pre-production -- preview --
branch. Before that, once the software packages have been created, they are uploaded to a
testing branch. The available automated deployment solution -- see Section \ref{subsec:sqa} -- checks
the installation and configuration of the component relying on the testing repository. On
successful completion, the packages are then automatically signed and subsequently moved to
the preview branch, from where they finally be made available in the production branch after
the release manager supervises the process.
